---
title: "Final Project"
author: "Team 5"
date: "2023-11-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = TRUE)
knitr::opts_chunk$set(messag = FALSE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning =  FALSE)
```
Install packages and libraries for our final project
```{r}
install.packages('prais')
```

Import libraries
```{r}
library(lmtest)
library(sandwich) 
library(stargazer)
library(tidyverse)
library(prais)
library(dplyr) #be able to use mutate function
```
Set working directory and read in data
```{r}
rawdata <- read.csv("all_data.csv")
```
#Real_GDP: Monthly version unit: Annualised change.
```{r}
head(rawdata)
tail(rawdata)
```


```{r}
stargazer(rawdata,type = 'text')

``` 
```{r}
cor(rawdata)
```

```{r}
new_dat <- mutate(rawdata,
                   Income_Per_Capita = Real_Disposable_Income/Population,
                   logipc = log(Income_Per_Capita),
                  loghpi = log(House_Price_Index)
                  )
new_data  <- na.omit(new_dat)
head(new_data)
```

```{r}
model1 = lm(loghpi ~ Stock_Price_Index, data =new_data)
summary(model1)
```


```{r}
model2 = lm(loghpi ~ Consumer_Price_Index, data =new_data)
summary(model2)

```


```{r}

model3 = lm(loghpi ~ Mortgage_Rate, data =new_data)
summary(model3)
```

```{r}
model4 = lm(loghpi ~ Real_Interest_Rate, data =new_data)
summary(model4)
```

```{r}
model5 = lm(loghpi ~ logipc, data =new_data)
```


```{r}
summary(model5)
```
```{r}
stargazer(model1, model2, model3, model4, model5, type = "text")
```


```{r}
model6 = lm(loghpi ~ logipc + Unemployment_Rate, data = new_data)
summary(model6)
```

```{r}
stargazer(model5,model6, type = "text")
```

```{r}
cor(new_data)
```


```{r}

plot(new_data$Date, model5$residuals,main  = "Statistic Model: Residuals Over time", xlab = "Year", ylab = "Residuals", data = new_data)
plot(new_data$Date, model6$residuals,main  = "Statistic Model: Residuals Over time", xlab = "Year", ylab = "Residuals", data = new_data)

```


```{r}
new_data$residuals <- resid(model6)

new_data
```

```{r}
RHAT <- resid(model6, data = new_data)
```

```{r}
dwtest(model6, alternative = "two.sided")

bgtest(model6, order = 1)
```
III Next step will be to conduct a hypothesis test to determine if these findings are the same as the DW test.

H0: no autocorrelation
H1: autocorrelation present
```{r}
new_data$LRHAT <- lag(RHAT, 1)

plot(new_data$LRHAT, model6$residuals,main  = "AR1", xlab = "Residuals Lag", ylab = "Residuals", data = new_data)
AR1 <- lm(RHAT ~ LRHAT, data = new_data)
summary(AR1)
```

IV Correcting for the autocorrelation: First Differencing Method

```{r}
new_data$LRHAT <- lag(RHAT, 1)
betahats <- coef(AR1)
RHO <- betahats[2]
new_data$diffhpi <- new_data$loghpi- RHO*lag(new_data$loghpi, 1)
new_data$diffunempr <- new_data$Unemployment_Rate - RHO*lag(new_data$Unemployment_Rate, 1)
new_data$diffipc <- new_data$Income- RHO*lag(new_data$logipc, 1)
model7 <- lm(diffhpi ~ diffipc + diffunempr, data = new_data)
summary(model7)
dwtest(model7)
```
```{r}
stargazer(model6,model7, type = "text")
```

```{r}
pw <- prais_winsten(formula = loghpi ~ logipc + Unemployment_Rate, data = new_data, index = new_data$date)
summary(pw)
```
```{r}
dwtest(pw)
bptest(pw)
```


```{r}
install.packages("sandwich")
install.packages("lmtest")
```
```{r}
library(sandwich)
library(lmtest)
model8 <-coeftest(model6, vcov = NeweyWest)
stargazer(model6,model8, type = "text")
```
 
Test for Homoscesdasticity 
```{r}
# residual
new_data$RHAT2<-resid(model6)^2
u2model<- lm(RHAT2 ~ logipc + Unemployment_Rate, data=new_data)
summary(u2model)
```
```{r}
bptest(model6)
```

```{r}
#Ho: Homoscedasticity  
#Ha: Heteroscedasticity
bptest(model6)
##Solution: Robust standard error

modfinal<-coeftest(model6,sandwich)
modfinal

#stargazer output with both robust SEs
robust.covariancemtx <- sandwich(model6)
robust.se <- sqrt(diag(robust.covariancemtx))
stargazer(model6, modfinal, se=list(NULL,robust.se), type="text")
```



